High-Performance Data Analysis on JANUS using Apache Spark

### 2013-12-18 paper.tex
More conclusion

\section{Conclusion}
We found that, while Spark offers an appealing abstraction layer for
data-parallel programming, achieving reasonable scalability even on trivial
problems is still very difficult. Without adequate profiling tools, we found
ourselves puzzled by the lackluster results of our experiments. With more time,
we could probably use the Spark logs to better understand where our serial
bottlenecks are and increase efficiency. It may very well still be worth
exploring how Spark could be used on JANUS, but it may require rethinking
how we are using the network and filesystems for this task.

>>>>

\section{Conclusion}
We found that, while Spark offers an appealing abstraction layer for
data-parallel programming, achieving reasonable scalability even on trivial
problems is still very difficult. Any abstraction for parallelism would
seemingly run into this problem: when speedups are not as expected, it is often
much harder to track down the source of the problem.  The lack of adequate
profiling tools made the lackluster results of our experiments all the more
puzzling. With more time, we could probably use the Spark logs to better
understand where our serial bottlenecks are and increase efficiency. It may
very well still be worth exploring how Spark could be used on JANUS, but it may
require rethinking how we are using the network and filesystems for this task.
